Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Abstract hacking.

\begin{abstract}
\vp{This abstract is quite long}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Domain fronting enables communication that is apparently with an allowed domain,
but actually with a forbidden domain.
The key idea is the use of different domain names at different layers of communication.
One domain is used on the ``outside'' of an HTTPS request---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---in the HTTP Host header, invisible to the
censor under HTTPS encryption.
We identify a number of hard-to-block web services,
like content delivery networks and Google,
that support fronting because they ignore the outside of an HTTPS request
and dispatch it internally according to the Host header.
If a censor is unable to distinguish fronted circumvention traffic and non-fronted ordinary traffic,
then blocking fronted traffic means blocking an entire web service,
resulting in expensive collateral damage.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek combines
fronting with an HTTP-based tunneling proxy
that decodes a sequence of HTTP requests and feeds their contents into Tor.
A censor sees only a sequence of HTTPS requests to an allowed domain.
We describe our experience with deploying \meek.
% \meek, or something based on it,
% has been adopted by other circumvention systems including
% [blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

Hiding the endpoint and obscuring byte patterns are important parts of blocking resistance,
but there are other, more subtle considerations.
We describe what we have done to disguise traffic ``tells'' in \meek,
including using a real web browser to make fronted HTTPS requests
in order to disguise the TLS fingerprint.
We argue that these measures, combined with domain fronting, increase the censor's effort
beyond simple one-shot blocking techniques such as IP address blacklisting, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}

@@

% VPN arms race We seek to build a system that remains difficult to block even
% after it has many users.

>>>>

\begin{abstract}
We describe ``domain fronting,'' a versatile censorship circumvention technique
that hides the remote endpoint of a communication.
Domain fronting works at the application layer, using HTTPS,
to communicate with a forbidden host
while appearing to communicate with some other host,
permitted by the censor.
The key idea is the use of different domain names at different layers of communication.
One domain appears on the ``outside'' of the HTTPS request---in the DNS request and
TLS Server Name Indication---while another domain appears
on the ``inside''---in the HTTP Host header, invisible to the
censor under HTTPS encryption.
A censor, unable to distinguish fronted and non-fronted traffic to a domain,
must choose between allowing circumvention traffic
and blocking the entire domain,
which results in expensive collateral damage.

Domain fronting is easy to deploy and use and does not require
special cooperation by network intermediaries.
We identify a number of hard-to-block web services,
such as content delivery networks,
that support domain-fronted connections
and are useful for censorship circumvention.
Domain fronting in various forms is now a circumvention workhorse.
We describe several months of deployment experience
in the Tor, Lantern, and Psiphon circumvention systems,
including user adoption, performance,
ongoing cost of operation, and lessons learned.
\end{abstract}

@@
